---
output: html_document
---
```{r include=FALSE, message=FALSE}
setwd("/Users/sunevan/Dropbox/Spring 2017/Text As Data/HW3")
library(quanteda)
library(quantedaData)
library(lda)
library(stm)
library(topicmodels)
library(tidytext)
library(ggplot2)
library(reshape2)
library(dplyr)
library(geometry)
library(Rtsne)
data("data_corpus_immigrationnews", package = "quantedaData")
```


###3(a)
```{r}
Q3CorpSub <- corpus_subset(data_corpus_immigrationnews,paperName %in% c("guardian","telegraph")) 

Q3_df <- data.frame(text = Q3CorpSub$documents$texts,
                    day = as.numeric(Q3CorpSub$documents$day),
                    paperName = Q3CorpSub$documents$paperName)

load("custom_stopwords.RData") 

Q3 <- textProcessor(Q3_df$text, metadata = Q3_df, removestopwords = FALSE,  removepunctuation = TRUE,stem = F, customstopwords = custom_stopwords)

```

###3(b)
```{r}
Q3_prep <- prepDocuments(Q3$documents,Q3$vocab, Q3$meta, lower.thresh = 30)
set.seed(10012)
stm30 <- stm(Q3_prep$documents,Q3_prep$vocab,0,prevalence=~Q3_df$paperName + as.numeric(Q3_df$day),init.type = "Spectral", content = ~Q3_df$paperName)
```
###3(c)

```{r}
knitr::opts_chunk$set(fig.width=30, fig.height=20)
plot(stm30,type = "summary")
```
```{r}
labelTopics(stm30,c(10,17,39,8,21))
```
#####Topic 10: "UKIP in Elections"
#####Topic 17: "Coalition"
#####Topic 39: "Migration from EU"
#####Topic 7: "Brokenshire's view on labor"
#####Topic 43: "Entertainment"

###3(d)
```{r}
Q3_prep$meta$day <- as.integer(Q3_prep$meta$day)
day <- as.numeric(Q3CorpSub$documents$day)
prep<-estimateEffect(c(10) ~ s(day) , stm30)
plot(prep, "day", stm30, topics = c(10), method = "continuous")

```
##### This topic moved up over the time. It started pretty low and got an increase at the end. 


```{r}
plot(stm30, type="perspectives",topics = c(10))
```
##### Guardian focus more on UKIP's information, campaign, their leader, and who are the suppoters and Telegraph cares more about if people for UKIP and win the election.
